Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-03-03 papers/CADE19/paper.tex
numbers

\section{Conclusions and Future Work}
\label{sec:conclusions}

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with other Solvers}

\begin{table}[t]
\caption{Total number of problems solved compared to other solvers.\label{tab:other}}
\centering
\begin{tabular}{l|l|l}
Solver 		& Total solved & Uniquely solved \\ \hline
Vampire (old)	& 13,057 & \\
Vampire (new)   & 13,191 & \\
E 			&10,845\\
iProver		& 8,143\\
CVC4		& 9,354\\
\end{tabular}
\end{table}

To place these results in context, we compare the overall number of problems solved by our new strategies with the results of other solvers (using their 2018 CASC competition strategy). These results are from 300s and are given in Table~\ref{tab:other}. In this table Vampire (old) stands for the 2018 competition version whilst Vampire (new) stands for the union of all problems solved by new options in the previous section. The main point we want to make here is that the unique problems found in the previous section remain unique when compared to other competitive solvers.

%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}
